---
title: "Introduction to fars"
author: "Federico Sensi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The package provides a set of functions to manage the data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing  the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 
When you work with `fars accident data` you want tso:

- Read the data for a specific year
- Summarize accident's data for one or more years
- Visualize accident on a map

Fars provides a set of functions to simplify this.

**NOTE:** Be sure working directory (setwd()) is set to the path containing the fars data file


## Functions
Fars aims to provide a function for each basic functionatility:
* `fars_read_years()` to read raw data from the accidents.
* `fars_summarize_years()` to summarizes yearly accidents data by month.
* `fars_map_state()` creates a plot with a state map including the accidents location by year.

### Read raw data with `fars_read_years()`

The `fars_read_years()` is used to load raw data:

```{r eval = FALSE}
# Select a single year
fars_one_year <- fars_read_years(2013)

# Select multiple years
fars_two_years <- fars_read_years(c(2013,2014))

```

### Summarize data with `fars_summarize_years()`

The `fars_summarize_years()` is used to summarize raw data:

```{r eval = FALSE}
# Summarize one years
fars_summ <- fars_summarize_years(2013)

# Summarize two years
fars_summs <- fars_summarize_years(c(2013, 2014))


```

### Visualize data with `fars_map_state()`

The `fars_map_state()` is used to visualize fars data:

```{r eval = FALSE}
# Visualize one years
fars_map_state(1,2013)


```

